---
title       : Develop Data Products Project
subtitle    : Shiny Application Presentation
author      : Ji Gu
job         : 
framework   : io2012        # {io2012, html5slides, shower, dzslides, ...}
highlighter : highlight.js  # {highlight.js, prettify, highlight}
hitheme     : tomorrow      # 
url:
  assets: ../../assets
widgets     : []            # {mathjax, quiz, bootstrap}
mode        : selfcontained # {standalone, draft}
knit        : slidify::knit2slides
---

## Structure of the dataset
The purpose is to examine relationships between numeric variables grouped by discrete variables in 'mtcars' dataset. The structure of the dataset is as follows 
```{r}
library(car);car<-mtcars;str(car)
```

---

## Default configuration
There are several default configurations in the user input part of the shiny application
  * Numeric variables ('mpg','disp','hp','drat','wt'and 'qsec') for x-axis and y-axis selection
  * Discrete variable ('vs','am','gear','carb' and 'cyl') as factor variables to seperate data into different categories for coloring and corresponding smoothing
  * Default smoothing method selection is 'Regression line'
  * Default confidence level is set at 0.95
  * Default degree of smoothing (only for LOESS smoothing) is set at 0.75
  * Default setting for 'Display confidence interval around smooth?' is off
  * Degree of smoothing (only for LOESS) - default=0.75
  * Trend line confidence level - default =0.95
  * Dispaly confidence interval around smooth - default = off

---

## Smoothing method options available
Two smoothing methods can be selected to explore relationship between the numeric variables from 'mtcars' dataset
  * Locally weighted scatterplot smoothing (LOESS) as data size is <1000
  * Linear Regression  


---

## Sample plot (slight difference from Shiny application)
```{r echo=FALSE}
library(ggplot2)
p<-ggplot(mtcars,aes(hp,mpg,gear))
p+geom_point(aes(color=factor(gear)))+stat_smooth(method="lm",aes(fill=factor(gear)),formula=y~x,level=0.95,se=TRUE)+ggtitle("mpg vs hp color by gear: smooth method lm")

```

  Smoothing method='Regression line', Confidence level=0.95
 
  



